\section{Requirements Traceability}
	\subsection {Log In, Sign Up and Data Editing}

		\subsubsection{System Registration}
		The Sign Up function is implemented by the ClientManager. Using the User Access interface, that has the method PARLACOLDB, it comunicates with the UserDataManager and saves the new User's data.
		
		\subsubsection{User LogIn}
		The LogIn is performed by the ClientManager that, as in the Sign Up, communicates with the UserDataManager through the User Access Interface. Here the AuthManager verifies the correspondance between the info inserted by the Customer and the ones stored in the DataBase using the DBAccess Interface with the method ÈGIUSTOONO and answers to the ClientManager.
		
		\subsubsection{User edit information}
		Similarly to the LogIn function the ClientManager communicates with the Data Manager. Here the Profile Editor, through the DBAccess Interface's method CAMBIADATI updates the User's data.
		
		\newpage
	\subsection {Registered User Requirements}
	
		
		\subsubsection{Instant Calls}
		This function is implemented by the Ride Controller, that recieved a request from a Client via the Ride Creation Interface, creates a Ride, looks for Taxi Drivers that may accept the jobs and reports it to them. The Controller also communicates with the DataBase to store the Ride's infos. \askpippo
		
		\subsubsection{Booking and Sharing}
		In this case the Ride Controller behaves the same way as the Instant Calls, with a difference: in case of a Shared Ride it passes the Ride to the Shared Ride Builder that will compose the sharing.
		
		\subsubsection{Booking Editing}
		To modify a Ride's data the Client passes to the Ride Controller the new info. The Controller checks if the modification follows the rules and through the MODIFICARIDE method of the Data Modification Interface writes the new infos in the DataBase.
		
		
	\subsection {Taxi Driver Requirements}
	
		\subsubsection{Driver LogIn}
		The Driver's LogIn works the same way as the Customer's LogIn does.
		
		\subsubsection{Driver Work Settings}
		The Driver, through the UI Access interface, comunicates to the ClientManager the new set of his status. The Manager provides to pass the information to the QueueManager.
		
		\subsubsection{Driver Ride Acceptance and Ending}
		As in the previous case, the Driver comunicates his decision $($accept, refuse or end a ride$)$ through the UI Interface. \\ This information arrives to the QueueManager through the ClientManager and it will perform the adequate changes to the Driver's position in the queue.
