\section{Risks associated with the project}
  \subsection{Project Risk}
    Here is a brief description of risk we may have due to poor design.
    \begin{description}
      \item[Delays over expected deadlines:] the project may be harder than we estimated. This may couse a dealayed release or a realease of a non completed version.
      \item[Lack of experience:] the team may lack in programming experience this may couse an possible release delay.
      \item[cambiamenti durante lo sviluppo\askpippo] during development we may find our project guide line hard to be implemented and we have to restructure them.
      \item[Lack of comunication:] to develop this project in time the team need to comunicate problem founded, that can be hard becouse team members may work remotely, this may lead to misunderstanding.
          To minimize this we have to make a RASD and DD document to guide the development.
    \end{description}

    \begin{table}[h]
    \centering
        \begin{tabular}{| l | l | l |}
            \hline
            \textbf{Risk} & \textbf{Probability} & \textbf{Effects}  \\
            \hline
            Delays Over Expected Deadlines & High & Moderate \\
            \hline
            Lack of Experience & Hight & Moderate \\
            \hline
            \askpippo & Low & Moderate \\
            \hline
            Lack of Comunication & High & Moderate \\
            \hline
        \end{tabular}
        \caption{Evaluation of Project risks.}
    \end{table}

  \subsection{Technical Risk}
  Here is a brief description of risk we may have due to poor implementation.

    \begin{description}
      \item[Server downtime:] we may underestimate the system load, found
          software bugs, this can couse a server downtime. We can workaround
          the software bugs by taking test and the system load by using third party cloud-base server.
      \item[Market reach:] the city user may don't use our taxi service, we can
          try to solve it by hiring a adviser, this would increase the cost.
      \item[Data security:] we can have data lost or leaked by hardware failure,
          software bugs, third party attack. We can workaround
          this by use security  standard for our software and testing it.
      \item[Scalability:] the system could have problem with a larger number of users, we can use a third party cloud server
          to host our system and simplify the expansions.
      \item[Bad code:] the code on large project may become hard to read/undertand, we can avoid this by
          write a Desing Document to guide our development.
    \end{description}

    \begin{table}[h]
      \centering
          \begin{tabular}{| l | l | l |}
              \hline
              \textbf{Risk} & \textbf{Probability}  & \textbf{Effects}  \\
              \hline
              Server Downtime & Moderate & High\\
              \hline
              Market Reach & Moderate & Moderate\\
              \hline
              Data Security & Moderate & High\\
              \hline
              Scalability & Low & Moderate          \\
              \hline
              Bad Code & Moderate & Moderate\\
              \hline
          \end{tabular}
        \caption{Evaluation of technical risks.}
    \end{table}
  \subsection{Economical Risk}
  \askpippo
    \begin{description}
      \item[Bankruptcy] the city may withdraw their offer. We can't avoid this.
      \item[Wrong cost evaluation] the cost may exceed our budget. To prevent this we may run a very in-depht analisys to prevent this risk.
    \end{description}

    \begin{table}[h]
\centering
    \begin{tabular}{| l | l | l |}
        \hline
        \textbf{Risk}                   & \textbf{Probability}  & \textbf{Effects}  \\
        \hline
        Bamkruptcy & Low & High \\
        \hline
        Wrong Cost Evaluation & Moderate & High \\
        \hline
    \end{tabular}
    \caption{Evaluation of economical risks.}
\end{table}
