\section{Task Schedule}
The tasks that we have to complete for this project can be divided in:
\begin{enumerate}
\item Deliver the main documents concerning the project such as:
	\begin{itemize}
		\item The \textit{Requirement Analysis and Specification Document} $($RASD$)$ containing the domain assumptions, the goals and the requirements of our project.
		\item The \textit{Design Document} $($DD$)$ that contains the explanation of the architecture of our system.
		\item The \textit{Integration Testing Plan Document} containing the plan of integration testing on our system.
		\item This \textit{Project Plan}
	\end{itemize}
\item A short presentation about the previous documents
\item Implement the following parts of the service:
	\begin{itemize}
		\item The application front-end for both mobile and web platforms.
		\item The ride management system.
		\item The ride reservation system.
		\item The user management system.
	\end{itemize}
\item Unit and Integration testing, which can be done iteratively as each part of the service is developed, and can be actively used as development feedback before release.
\end{enumerate}

The tasks to be performed do not require a strict order, especially with regards to the development of the software. However, we did generate a dependecy graph to show what parts have
to be completed before work can be started on other parts. The dependency graph is pictured below.



%GRAPH


Due to the nature of our project, there are several fixed deadlines with regards to the delivery of most documents. However, the development and testing cycle has no set deadlines 
yet, since it is too early in the development cycle to assess the amount of time necessary to develop each part of the software.

\begin{table}
    \centering
    \begin{tabular}{| l | l | l |}
        \hline
        \textbf{Activity}   & \textbf{Start Date}   & \textbf{Deadline} \\
		\hline
        Project Plan				& 29/09/2015		& 14/10/2015\\
        \hline
        RASD						& 15/10/2015		& 06/11/2015\\
		\hline
        DD							& 07/11/2015		& 04/12/2015\\
		\hline
        ITPD						& 10/12/2015		& 05/01/2016\\
		\hline
		Implementation and Testing	& 08/01/2016		& 29/07/2016\\
        \hline
        Presentation				& 10/02/2015		& 15/02/2015\\
		\hline
        
    \end{tabular}
    \caption{Schedule for project tasks.}
    \label{tab:schedule}
\end{table}